Project Protocol

### 2019-10-21 protocol.Rmd
procedures

##	Recruitment strategies, timeframe 
Recruitment will take place via advertising on the Figure-Eight dashboards.
The Figure-Eight platform will advertise this as a “job” to potential participants, they will not be under any obligation to complete this task. We will have the opportunity to wait until enough participants have completed the survey and provided their responses.

@@

##	Participant withdrawal
Participants will be able to withdraw by leaving the survey at any time.

@@

##	Screening of participants
Participants will need to have achieved contributor level two on the Figure-Eight platofrm, this is a smaller group of more experienced, higher accuracy contributors.
Test questions are the most important quality control mechanism in the Figure-Eight Platform. Participants will complete them to practice and prepare for the experiment questions, they will need to reach an accuracy threshold we will set, to be allowed to participate in answering the experiment survey questions.

Contributors that fail quiz mode are not paid and are permanently disqualified from working on your job. Participants will need to reach an accuracy threshold we will set to be allowed to answer the questions in our survey. Test questions will also be included as the job progresses so we can be sure quality remains high.

>>>>

##	Recruitment strategies, timeframe 
Recruitment will take place via advertising on the Figure-Eight dashboards.
The Figure-Eight platform will advertise this as a "job" to potential participants, they will not be under any obligation to complete this task. We keep advertising until enough participants have completed the survey, then remove the advertisements and close the survey.

@@

##	Participant withdrawal
Participants can withdraw from the experiment at any time by quitting the survey.

@@

##	Screening of participants

Participants will need to have achieved contributor level two on the Figure-Eight platofrm, this is a smaller group of more experienced, higher accuracy contributors.

Test questions are the most important quality control mechanism in the Figure-Eight Platform. Participants will complete them to practice and prepare for the experiment questions, they will need to reach an accuracy threshold we will set, to be allowed to participate in answering the experiment survey questions.

The Figure Eight procedures are followed: *Contributors that fail quiz mode are not paid and are permanently disqualified from working on your job. Participants will need to achieve a pre-determined accuracy threshold to be allowed to answer the questions in our survey.*
